\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-16 acknowledgements.tex
add title page and convert to book format
fix the infinite loop thing; add figures
acknowledge pdl

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save this for last :)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save this for last :)

Thanks to Deb Cavlovich, for holding on to this thesis for a few days more for Ben to finish it properly.

Thanks to my advisor, too, I guess, and maybe also to the people I worked with and my friends as well.

Thanks to the members and companies of the PDL Consortium (including Actifo,
APC, EMC, Emulex, Facebook, Fusion-io, Google, Hewlett-Packard, Hitachi, Huawei
Technologies, Intel, Microsoft, NEC, NetApp, Oracle, Panasas, Riverbed,
Samsung, Seagate, STEC, Symantec, VMware, and Western Digital) for their
interest, insights, feedback, and support.
